---
title: "Illusion Game Reliability"
subtitle: "Factor Structure"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr",
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)

cache <- TRUE
runModels <- TRUE
bestModels <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/5_Structure-",
  fig.width = fig.width,
  fig.height = fig.height
)
```


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)
library(lavaan)
library(ggraph)
library(tidySEM)
```

# Perceptual Task

```{r message=FALSE, warning=FALSE}
perceptual <- read.csv("../data/scores_perceptual.csv") |> 
  select(-contains("Sigma")) |> 
  select(-contains("Beta")) |> 
  # mutate(across(ends_with("_Error"), \(x) -1*x)) |>  # So that higher score = More errors
  mutate(across(ends_with("Intercept_Error"), \(x) -1*x)) |>  # Not the intercept (re-reverse)
  mutate(across(ends_with("_RT"), \(x) -1*x)) |>  # So that higher score = Longer RTs
  mutate(across(ends_with("Intercept_RT"), \(x) -1*x))  # Not the intercept (re-reverse)

for(i in names(perceptual)[names(perceptual) != "Participant"]) {
  perceptual[check_outliers(perceptual[[i]], method = "zscore_robust", threshold = 5), i] <- NA 
}

perceptual <- standardize(perceptual) |> 
   mutate(across(where(is.numeric), as.numeric))
```

## Distribution

```{r message=FALSE, warning=FALSE}
perceptual |> 
  estimate_density(method = "kernSmooth") |> 
  separate(Parameter, into = c("Task", "Type", "Parameter", "Model")) |> 
  ggplot(aes(x=x, y=y, color=Type, linetype = Parameter)) +
  geom_line(linetype = 2) +
  facet_grid(Parameter~Model)
```

## Correlation


```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
cor <- correlation::correlation(perceptual, redundant = TRUE, p_adjust = "none")

p_data <- cor |>
  mutate(Parameter1 = str_replace_all(str_remove(Parameter1, "Perception_"), "_", " "),
         Parameter2 = str_replace_all(str_remove(Parameter2, "Perception_"), "_", " ")) |>
  correlation::cor_sort(hclust_method = "ward.D2") |>
  cor_lower() |>
  mutate(
    Text = insight::format_value(r, zap_small = TRUE, digits = 3),
    Text = str_replace(str_remove(Text, "^0+"), "^-0+", "-"),
    Text = paste0(Text, insight::format_p(p, stars_only = TRUE)),
    Parameter2 = fct_rev(Parameter2)
  )


p_data |> 
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label = Text), size = rel(2), alpha=2/3) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(title = "Correlation Matrix of Perceptual Task Scores", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# heatmap(as.matrix(cor))
```


## Factor Analysis

### First Level

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
rez <- parameters::n_factors(select(perceptual, -Participant), n_max=15)
rez
plot(rez)

fa <- parameters::factor_analysis(select(perceptual, -Participant),
  # cor = as.matrix(cor),
  n = 3,
  rotation = "oblimin",
  fm = "mle",
  sort = TRUE
)

insight::print_md(fa)

plot(fa) +
  theme_minimal()
# psych::omega(data, fm = "mle", nfactors=7)
# fa <- psych::fa.multi(as.matrix(cor), nfactors = 3, nfact2 = 1, n.obs = nrow(random))
# psych::fa.multi.diagram(fa)
```

### Second Level

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
data <- predict(fa)

# rez <- parameters::n_factors(data, rotation = "varimax")
# plot(rez)

fa2 <- parameters::factor_analysis(data,
  n = 1,
  rotation = "varimax",
  fm = "mle",
  sort = TRUE
)

insight::print_md(fa2)
```



## Sructural Equation Model

### Level 1

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
fit_sem <- function(model, data, ...) {
  sem(model = model,
      data  = data[complete.cases(data), ],
      bounds = "standard",
      estimator = "ML",
      auto.fix.first=TRUE, 
      control=list(iter.max=200000, eval.max = 20000), 
      ...) 
}


names <- names(select(perceptual, -Participant))
data <- setNames(as.data.frame(str_split_fixed(names, "_", 4)), c("Task", "Illusion_Type", "Parameter", "Outcome"))
data$Name <- names

# Model 0 - by EFA
by_efa <-  efa_to_cfa(fa, threshold = "max")
# cat(by_model)
m0 <- fit_sem(by_efa, data=perceptual)

# Model 1 - by Model
by_model <-  paste(sort(paste0("p_", ifelse(str_detect(data$Outcome, "RT"), "RT", "Error"), " =~ ", data$Name)), collapse = "\n")
# cat(by_model)
m1 <- fit_sem(by_model, data=perceptual)

# Model 2 - by Component
by_component <-  paste(sort(paste0("p_", data$Outcome, " =~ ", data$Name)), collapse = "\n")
# cat(by_component)
m2 <- fit_sem(by_component, data=perceptual)

# Model 3 - by Type
by_type <-  paste(paste(paste0(data$Illusion_Type), "=~", data$Name), collapse = "\n")
# cat(by_type)
m3 <- fit_sem(by_type, data=perceptual)

# Model 4 - by Parameter
by_param <-  paste(paste(paste0(data$Parameter), "=~", data$Name), collapse = "\n")
# cat(by_param)
m4 <- fit_sem(by_param, data=perceptual)

# Model 4 - Unique
m5 <-  fit_sem(paste0("p =~ ", paste(names, collapse = " + ")), data=perceptual)


anova(m2, m0, m1, m3, m4, m5)
test_bf(m2, m0, m1, m3, m4, m5)
```

<!-- ### Improvements -->

<!-- ```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE} -->
<!-- by_model2 <- paste(sort(paste0("p_", case_when( -->
<!--   str_detect(data$Outcome, "BetaRT") ~ "BetaRT", -->
<!--   str_detect(data$Outcome, "RT") ~ "RT", -->
<!--   TRUE ~ "Error" -->
<!--   ), " =~ ", data$Name)), collapse = "\n")  -->

<!-- m0mod <- fit_sem(by_model2, data=perceptual) -->

<!-- anova(m0, m0mod) -->
<!-- test_bf(m0, m0mod) -->
<!-- ``` -->

### Common Factor

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
# One factor
m2b <- fit_sem(paste0(by_component, "\np =~ p_RT + p_Error"), data=perceptual)

anova(m2, m2b)
test_bf(m2, m2b)
compare_performance(m2, m2b, metrics = c("RMSEA", "NFI", "CFI"))
```

### Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE, fig.width=20, fig.height=20}
summary(m2, standardize = TRUE, fit.measures = TRUE)
graph_sem(m2, layout = get_layout(m2, layout_algorithm = "layout_with_lgl")) 
```

### Scores Extraction

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
scores_p <- mutate(as.data.frame(predict(m2)), Participant = perceptual$Participant[complete.cases(perceptual)])
```


### Empirical Scores

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
empirical <- read.csv("../data/preprocessed_perceptual.csv")

empirical <- empirical |> 
  group_by(Participant, Illusion_Type) |> 
  summarize(Empirical_Errors = as.numeric(sum(Error, na.rm=TRUE))) |> 
  full_join(
    empirical |> 
      filter(Error == 0) |> 
      group_by(Participant, Illusion_Type) |> 
      summarize(Empirical_MeanRT = mean(RT, na.rm=TRUE)), by = c("Participant", "Illusion_Type")) |> 
  ungroup() |> 
  pivot_wider(names_from = "Illusion_Type", values_from = c("Empirical_Errors", "Empirical_MeanRT")) |> 
  left_join(scores_p, by = "Participant") |> 
  left_join(perceptual, by = "Participant")

correlation::correlation(select(empirical, starts_with("Empirical")), select(empirical, -Participant, -starts_with("Empirical"))) |> 
  summary() |> 
  plot() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Illusion Task

```{r message=FALSE, warning=FALSE}
illusion <- read.csv("../data/scores_illusion1.csv") |> 
  select(-contains("Diff")) |> 
  select(-contains("Interaction")) |>
  select(-contains("Sigma")) |> 
  select(-contains("Beta")) 
  # mutate(across(ends_with("_Error"), \(x) -1*x))  # So that higher score = More errors

for(i in names(illusion)[names(illusion) != "Participant"]) {
  illusion[check_outliers(illusion[[i]], method = "zscore_robust", threshold = 5), i] <- NA 
}

illusion <- standardize(illusion) |> 
   mutate(across(where(is.numeric), as.numeric))
```

## Distribution

```{r message=FALSE, warning=FALSE}
illusion |> 
  estimate_density(method = "kernSmooth") |> 
  separate(Parameter, into = c("Type", "Parameter", "Model")) |>
  ggplot(aes(x=x, y=y, color=Type)) +
  geom_line(linewidth=1) +
  facet_grid(Model ~ Parameter, scales = "free") 
```

## Correlation


```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
cor <- correlation::correlation(illusion, redundant = TRUE, p_adjust = "none")

p_data <- cor |>
  correlation::cor_sort(hclust_method = "ward.D2") |>
  cor_lower() |>
  mutate(
    Text = insight::format_value(r, zap_small = TRUE, digits = 3),
    Text = str_replace(str_remove(Text, "^0+"), "^-0+", "-"),
    Text = paste0(Text, insight::format_p(p, stars_only = TRUE)),
    Parameter2 = fct_rev(Parameter2)
  )


p_data |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label = Text), size = rel(4), alpha=3/3) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(title = "Correlation Matrix", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# heatmap(as.matrix(cor))
```

## Factor Analysis

### First Level

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
rez <- parameters::n_factors(select(illusion, -Participant), n_max=9)
rez
plot(rez)

fa <- parameters::factor_analysis(select(illusion, -Participant),
  # cor = as.matrix(cor),
  n = 2,
  rotation = "oblimin",
  fm = "mle",
  sort = TRUE
)

insight::print_md(fa)

plot(fa) +
  theme_minimal()
# psych::omega(data, fm = "mle", nfactors=7)
# fa <- psych::fa.multi(as.matrix(cor), nfactors = 3, nfact2 = 1, n.obs = nrow(random))
# psych::fa.multi.diagram(fa)
```

### Second Level

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
# data <- predict(fa)
# 
# rez <- parameters::n_factors(na.omit(data), rotation = "oblimin")
# plot(rez)
# 
# fa2 <- parameters::factor_analysis(data,
#   n = 2,
#   rotation = "oblimin",
#   fm = "mle",
#   sort = TRUE
# )
# 
# insight::print_md(fa2)
```


## Sructural Equation Model

### Level 1

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
names <- names(select(illusion, -Participant))
data <- setNames(as.data.frame(str_split_fixed(names, "_", 3)), c("Illusion_Type", "Parameter", "Outcome"))
data$Name <- names

# Model 1 - EFA
by_efa <- efa_to_cfa(fa, threshold = "max")
m1 <- fit_sem(by_efa, data=illusion)

# Model 2 - by Model
by_model <-  paste(sort(paste(data$Outcome, "=~", data$Name)), collapse = "\n")
# cat(by_model)
m2 <- fit_sem(by_model, data=illusion)

# Model 3 - by Type
by_type <-  paste(paste(paste0(data$Illusion_Type), "=~", data$Name), collapse = "\n")
# cat(by_type)
m3 <- fit_sem(by_type, data=illusion)

# Model 4 - Unique
m4 <-  fit_sem(paste0("p =~ ", paste(names, collapse = " + ")), data=illusion)

anova(m1, m2, m3, m4)
test_bf(m1, m2, m3, m4)
```

### Common Factor

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
m5 <- fit_sem(paste0(by_type, "\ni =~ Ebbinghaus + MullerLyer + VerticalHorizontal"), data=illusion)

anova(m1, m5)
test_bf(m1, m5)
compare_performance(m1, m5, metrics = c("RMSEA", "NFI", "CFI"))
```

### Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
display(performance(m5))
summary(m5, standardize = TRUE, fit.measures = TRUE)
# graph_sem(m5, layout = get_layout(m5, layout_algorithm = "layout_with_lgl")) 
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE, fig.width=15, fig.height=15}
colors <- c("i" = "#9C27B0", 
            "Ebbinghaus"="#3F51B5",
            "VerticalHorizontal"="#FF5722",
            "MullerLyer" = "#4CAF50",
            "black"="black")

edges <- tidySEM::get_edges(m5) |> 
  mutate(color = ifelse(sign(as.numeric(est_std)) >= 0, "1", "-1"),
         width = abs(as.numeric(est_std)),
         type = ifelse(from == "i", "curved", "straight"),
         text = paste(est_std, confint_std)) |> 
  filter(lhs != rhs)

nodes <- tidySEM::get_nodes(m5) |> 
  mutate(angle = ifelse(grepl("_", name), 90, 0),
         hjust = case_when(
           grepl("_", name) ~ 1.5,
           name == "i" ~ 0.5,
           TRUE ~ 0.5),
         size = case_when(
           grepl("_", name) ~ 1,
           name == "i" ~ 7,
           TRUE ~ 6),
         textsize = case_when(
           grepl("_", name) ~ 1,
           name == "i" ~ 3,
           TRUE ~ 1.1),
         face = case_when(
           grepl("_", name) ~ "italic",
           name == "i" ~ "bold.italic",
           TRUE ~ "plain"),
         color = str_remove_all(label, " - .*"),
         textcolor = ifelse(grepl("_", name), "black", "white"),
         label = case_when(
           label == "MullerLyer" ~ "Müller-Lyer",
           label == "VerticalHorizontal" ~ "Vertical-\nHorizontal",
           str_detect(label, "_Error") ~ "Error",
           str_detect(label, "_RT") ~ "RT ",
           TRUE ~ label
         ),
         family = ifelse(name == "i", "serif", "sans"))


p_sem <- tidygraph::tbl_graph(nodes = nodes, edges = edges) |> 
  ggraph(layout = "sugiyama") +
  geom_edge_arc(aes(filter=type!="straight",
                    edge_width = width,
                    color = color,
                    label=est_std),
                strength = 0.03 * c(-1, 1, 1),
                angle_calc="along",
                label_dodge=unit(-0.017, "npc"),
                label_size = rel(8)) +
  geom_edge_link(aes(filter=type=="straight",
                     edge_width = width, 
                     color = color,
                     label=est_std), 
                 angle_calc="along", 
                 label_dodge=unit(-0.017, "npc"),
                 label_size = rel(8)) +
  geom_node_point(aes(shape = shape, color=color, size=size)) +
  geom_node_text(aes(label = label, angle = angle, hjust=hjust),
                 color=nodes$textcolor, 
                 fontface=nodes$face,
                 size = rel(nodes$textsize*10),
                 family=nodes$family) +
  scale_y_continuous(expand = expansion(add=c(0.5, 0.5))) +
  scale_edge_width_continuous(range=c(0.3, 6)) +
  scale_edge_color_manual(values=c("1"="#263238", "-1"="#B71C1C")) +
  scale_color_manual(values=colors, guide="none") +
  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
  scale_size_continuous(range = c(10, 95), guide="none") +
  guides(edge_colour = "none", edge_width = "none") + 
  labs(title = "Structural Equation Model")  +
  theme_graph() +
  theme(plot.title = element_text(hjust=0.5))

p_sem
ggsave("figures/figure_sem.png", p_sem, width=15, height=15)
# save(p_sem, file="models/p_sem.Rdata")
```


### Scores Extraction

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
scores_i <- mutate(as.data.frame(predict(m5)), Participant = illusion$Participant[complete.cases(illusion)]) 
```


### Empirical Scores

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
empirical <- read.csv("../data/preprocessed_illusion1.csv")

empirical <- empirical |>  
  filter(Illusion_Effect == "Incongruent") |> 
  group_by(Participant, Illusion_Type) |> 
  summarize(Empirical_Errors = as.numeric(sum(Error, na.rm=TRUE))) |> 
  full_join(
    empirical |> 
      filter(Illusion_Effect == "Incongruent", Error == 0) |> 
      group_by(Participant, Illusion_Type) |> 
      summarize(Empirical_MeanRT = mean(RT, na.rm=TRUE)), by = c("Participant", "Illusion_Type")) |> 
  ungroup() |> 
  pivot_wider(names_from = "Illusion_Type", values_from = c("Empirical_Errors", "Empirical_MeanRT")) |> 
  left_join(scores_i, by = "Participant") |> 
  left_join(illusion, by = "Participant")

correlation::correlation(select(empirical, starts_with("Empirical")), select(empirical, -Participant, -starts_with("Empirical"))) |> 
  summary() |> 
  plot() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
write.csv(full_join(left_join(scores_i, read.csv("../data/scores_illusion1.csv"), by = "Participant"), scores_p, by = "Participant"), "../data/scores_sem.csv", row.names = FALSE)
```


## Validation on New Set

<!-- Validation on session 2  -->

