---
title: "Illusion Game Reliability"
subtitle: "Factor Structure"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr",
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)

cache <- TRUE
runModels <- TRUE
bestModels <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/5_Structure-",
  fig.width = fig.width,
  fig.height = fig.height
)
```


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)
library(lavaan)
library(ggraph)

dfsub <- read.csv("../data/scores_sem.csv") |> 
  full_join(
    read.csv("../data/preprocessed_questionnaires.csv") |> 
    select(!ends_with("_SD") & !ends_with("_RT")), 
    by="Participant") |> 
  select(-starts_with("Item_"), -starts_with("AttentionCheck")) |> 
  mutate(
    Education = fct_relevel(Education, "Prefer not to say", "Other", "High school", "Bachelor", "Master", "Doctorate")
  ) |> 
  right_join(
    read.csv("../data/preprocessed_illusion1.csv") |> 
      select(Participant, Screen_Size, Screen_Refresh, Task_Order) |> 
      dplyr::distinct(),
    by = "Participant"
  )

# Variables
DVs <- c(
  "Ebbinghaus" = "#2196F3",
  "VerticalHorizontal" = "#FF5722",
  "MullerLyer" = "#4CAF50",
  "i" = "#9C27B0",
  "Ebbinghaus_Strength_Error" = "blue",
  "VerticalHorizontal_Strength_Error" = "red",
  "MullerLyer_Strength_Error" = "green",
  "Ebbinghaus_Interaction_Error" = "blue",
  "VerticalHorizontal_Interaction_Error" = "red",
  "MullerLyer_Interaction_Error" = "green"
)

DVs_p <- c(
  "p_Error" = "#FFC107",
  "p_RT" = "#F44336"
  # "p_BetaRT" = "#E91E63"
)
```

```{r message=FALSE, warning=FALSE}
prettify <- function(x) {
  x <- str_remove_all(x, "IPIP6_|PID5_|ASQ_|SPQ_|PHQ4_|MAIA_|IAS_|GCBS_|LIE_|PI_")
  case_when(
    x == "VerticalHorizontal" ~ "Vertical-Horizontal",
    x == "MullerLyer" ~ "Müller-Lyer",
    x == "i" ~ "Factor i",
    # Perceptual
    x == "p_RT" ~ "Perception (RT)",
    x == "p_Error" ~ "Perception (Error)",
    x == "p_BetaRT" ~ "Perception (Attention)",
    # Questionnaires
    x == "HonestyHumility" ~ "Honesty-Humility",
    x == "NegativeAffect" ~ "Negative Affect",
    TRUE ~ x
  )
}


make_correlation <- function(x, y) {
  # Base matrix
  r <- correlation::correlation(x,
    y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow",
    sort = TRUE
  ) 
  
  # Add Spearman
  cor <- r |>
    datawizard::data_remove(c("ROPE_Percentage"))
  cor$`BF (Spearman)` <- format_bf(
    correlation::correlation(
      x, y,
      bayesian = TRUE,
      ranktransform = TRUE,
      bayesian_prior = "medium.narrow"
    )$BF,
    name = NULL, stars = TRUE
  )

  cor <- cor |>
    select(-starts_with("Prior")) |> 
    arrange(desc(BF))
  
  table <- filter(cor, (BF > 3) | (BF < 1/10))
  if(nrow(table) == 0) table <- data.frame(Results = "No significant correlations.")
  
  list(r = cor, table = display(table), m = summary(r))
}


plot_correlation <- function(dfsub, x="I", y="IPIP6_Agreeableness", fill="grey") {
  param <- cor_test(dfsub, x, y, bayesian = TRUE, bayesian_prior = "medium.narrow")

  # Format stat output
  r <- str_replace(str_remove(insight::format_value(param$rho), "^0+"), "^-0+", "-")
  CI_low <- str_replace(str_remove(insight::format_value(param$CI_low, zap_small=TRUE), "^0+"), "^-0+", "-")
  CI_high <- str_replace(str_remove(insight::format_value(param$CI_high, zap_small=TRUE), "^0+"), "^-0+", "-")

  stat <- paste0("italic(r)~'= ", r, ", 95% CI [", CI_low, ", ", CI_high, "], BF'['10']~'", paste0(insight::format_bf(param$BF, name = "")), "'")

  label <- data.frame(x = min(dfsub[[x]], na.rm=TRUE),
                      y = max(dfsub[[y]], na.rm=TRUE))
  
  # Plot
  dfsub[c(x, y)] |> 
    na.omit() |> 
    ggplot(aes(x=!!sym(x), y=!!sym(y))) +
    geom_point2(size=3,
                  color = fill,
                  # color = DVs[x],
                  alpha=2/3) +
    geom_smooth(method="lm", color="black", formula="y ~ x", alpha=0.3)  +
    labs(y = prettify(y),
         x = ifelse(x == "I",
                    expression("Factor"~ italic(i)),
                    prettify(x))) +
    annotate("label", x = label$x, y = label$y, label = stat, parse=TRUE, hjust=0, vjust=1) +
      theme_modern() +
      ggside::geom_xsidedensity(fill=DVs[x], color="white") +
      ggside::geom_ysidedensity(fill=fill, color="white") +
      ggside::theme_ggside_void() +
      ggside::scale_ysidex_continuous(expand = c(0, 0)) +
      ggside::scale_xsidey_continuous(expand = c(0, 0))
}
```


# Perceptual


```{r, message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[names(DVs_p)], dfsub[names(DVs)])
r$r
plot(r$m)
```

# Contextual

## Screen Characteristics {.tabset}

### Illusion

```{r message=FALSE, warning=FALSE, cache=cache}
contextual <- make_correlation(dfsub[names(DVs)], dfsub[c("Screen_Size", "Screen_Refresh")])
contextual$table

dfsub |>
  select(Participant, all_of(names(DVs)), Screen_Size, Screen_Refresh) |> 
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score") |>
  na.omit() |> 
  ggplot(aes(x = Screen_Refresh, y = Score)) +
  geom_point2(aes(color = Index), alpha = 0.1, size = 2) +
  geom_smooth(aes(color = Index, group = Index, linetype = Index), se = FALSE, method = "lm", formula = 'y ~ x') +
  scale_x_continuous(expand = c(0, 0)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1)) +
  scale_linetype_manual(values = c("p_RT" = "solid", setNames(rep("dotted", 9), names(DVs)[!names(DVs) %in% c("p_RT")])), guide = "none") +
  scale_color_manual(values = DVs) +
  theme_modern() +
  labs(y = "Illusion Sensitivity", x = "Screen Rehresh Rate", linetype = "Significance", size = "Significance") +
  ggside::geom_xsidedensity(data = dfsub, fill = "grey", color = "white") +
  ggside::geom_ysidedensity(aes(y = Score, color = Index)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0))
```

### Perceptual

```{r message=FALSE, warning=FALSE, cache=cache}
contextual <- make_correlation(dfsub[names(DVs_p)], dfsub[c("Screen_Size", "Screen_Refresh")])
contextual$table
```

## Task Order 

```{r taskorder, message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for (i in c(names(DVs), names(DVs_p))) {
  model <- lm(paste0(i, " ~ Task_Order"), data = dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$ymiddle <- param$Coefficient[1] + diff(param$Coefficient) / 2
  param$BF <- parameters::parameters(BayesFactor::ttestBF(formula = as.formula(paste0(i, " ~ Task_Order")), data = dfsub[!is.na(dfsub[[i]]), ]))$BF
  params <- rbind(params, as.data.frame(param[2, ]))
}

data <- dfsub |>
  pivot_longer(all_of( c(names(DVs), names(DVs_p))), names_to = "Index", values_to = "Score") |>
  mutate(
    Index = fct_relevel(Index,  c(names(DVs), names(DVs_p))),
    Index = fct_relabel(Index, ~ prettify(.x)),
    Task_Order = as.factor(Task_Order)
  ) |> 
  select(Participant, Index, Score, Task_Order) |> 
  na.omit()


p_order <- data |>
  ggplot(aes(x = Index, y = Score)) +
  stat_slab(data = filter(data, Task_Order == "1"), aes(fill = Task_Order), side = "left", scale = 0.5, position = "dodge") +
  stat_slab(data = filter(data, Task_Order == "2"), aes(fill = Task_Order), side = "right", scale = 0.5, position = "dodge") +
  stat_pointinterval(aes(group = Task_Order), point_interval = "mean_qi", position = "dodge") +
  geom_text(data = mutate(params, sig = insight::format_bf(BF, stars_only = TRUE), Index = prettify(Index)), aes(label = sig, y = ymiddle), size = 6) +
  geom_label(
    data = mutate(params, label = insight::format_bf(BF, protect_ratio = TRUE, stars = TRUE), Index = prettify(Index)),
    aes(label = label), y = 2.7, size = 3
  ) +
  scale_fill_manual(values = c("1" = "blue", "2" = "orange")) +
  scale_x_discrete(labels = function(x) ifelse(x == "i", "Factor i", x)) +
  theme_minimal() +
  labs(fill = "", x = "Task Order", y = "Illusion Sensitivity", title = "Task Order") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5)
  )
p_order
# ggsave("figures/figure_sex.png", p_gender, width=15166, height=5000, bg="white", units = "px", limitsize = FALSE, scale = 0.3)
```


# Demographics

## Sex {.tabset}

### Illusion

```{r isex, message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for (i in names(DVs)) {
  model <- lm(paste0(i, " ~ Sex"), data = dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$ymiddle <- param$Coefficient[1] + diff(param$Coefficient) / 2
  param$BF <- parameters::parameters(BayesFactor::ttestBF(formula = as.formula(paste0(i, " ~ Sex")), data = dfsub[!is.na(dfsub[[i]]), ]))$BF
  params <- rbind(params, as.data.frame(param[2, ]))
}

format_table(params) |> 
  mutate(Parameter = "Female - Male") |> 
  display()

# Plot
data <- dfsub |>
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score") |>
  mutate(
    Index = fct_relevel(Index, names(DVs)),
    Index = fct_relabel(Index, ~ prettify(.x))
  ) |> 
  select(Participant, Index, Score, Sex) |> 
  na.omit()


p_gender <- data |>
  ggplot(aes(x = Index, y = Score)) +
  stat_slab(data = filter(data, Sex == "Male"), aes(fill = Sex), side = "left", scale = 0.5, position = "dodge") +
  stat_slab(data = filter(data, Sex == "Female"), aes(fill = Sex), side = "right", scale = 0.5, position = "dodge") +
  stat_pointinterval(aes(group = fct_rev(Sex)), point_interval = "mean_qi", position = "dodge") +
  geom_text(data = mutate(params, sig = insight::format_bf(BF, stars_only = TRUE), Index = prettify(Index)), aes(label = sig, y = ymiddle), size = 6) +
  geom_label(
    data = mutate(params, label = insight::format_bf(BF, protect_ratio = TRUE, stars = TRUE), Index = prettify(Index)),
    aes(label = label), y = 1, size = 3
  ) +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63"), guide = guide_legend(reverse = TRUE)) +
  theme_minimal() +
  labs(fill = "", x = "Sex", y = "Illusion Sensitivity", title = "Sex") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5)
  )

p_gender
# ggsave("figures/figure_sex.png", p_gender, width=15166, height=5000, bg="white", units = "px", limitsize = FALSE, scale = 0.3)
```


### Perceptual

```{r psex, message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for (i in names(DVs_p)) {
  model <- lm(paste0(i, " ~ Sex"), data = dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$BF <- parameters::parameters(BayesFactor::ttestBF(formula = as.formula(paste0(i, " ~ Sex")), data = dfsub[!is.na(dfsub[[i]]), ]))$BF
  params <- rbind(params, as.data.frame(param[2, ]))
}

format_table(params) |> 
  mutate(Parameter = "Female - Male") |> 
  display()
```



<!-- ## Age -->

<!-- ```{r age_stats, message=FALSE, warning=FALSE, cache=cache} -->
<!-- preds <- data.frame() -->
<!-- for (i in names(DVs)) { -->
<!--   gam <- brms::brm(paste0(i, " ~ s(Age)"), data = dfsub, refresh = 0) -->
<!--   model <- brms::brm(paste0(i, " ~ poly(Age, 3)"), data = dfsub, refresh = 0) -->

<!--   param <- parameters::parameters(model) -->
<!--   slopes <- estimate_slopes(gam, trend = "Age") -->

<!--   pred <- get_datagrid(gam, at = "Age", length = 50) -->
<!--   pred$Predicted <- get_predicted(gam, data = pred) -->

<!--   pred$ylabel <- pred$Predicted[50] -->
<!--   pred$Index <- i -->
<!--   pred$Effect <- slopes$Coefficient -->
<!--   pred$pd_gam <- slopes$pd -->
<!--   pred$pd_poly1 <- param$pd[2] -->
<!--   pred$pd_poly2 <- param$pd[3] -->
<!--   preds <- rbind(preds, pred) -->
<!-- } -->

<!-- preds |> -->
<!--   group_by(Index) |> -->
<!--   slice(1) |> -->
<!--   select(-Predicted, -Age) |> -->
<!--   arrange(desc(pd_gam)) -->

<!-- p_age <- preds |> -->
<!--   mutate( -->
<!--     pd_gam = format_pd(pd_gam, stars_only = TRUE), -->
<!--     pd_gam = ifelse(pd_gam == "", "NS", pd_gam) -->
<!--   ) |> -->
<!--   ggplot(aes(x = Age, y = Predicted)) + -->
<!--   geom_line(aes(color = Index, group = Index, linetype = pd_gam, size = pd_gam)) + -->
<!--   ggrepel::geom_label_repel( -->
<!--     data = preds |> -->
<!--       group_by(Index) |> -->
<!--       slice(1) |> -->
<!--       mutate(label = prettify_itemName(ifelse(Index == "i", "Factor i", Index))), -->
<!--     aes(y = ylabel, label = label, x = 69, color = Index), hjust = 0, direction = "y", -->
<!--     min.segment.length = 3 -->
<!--   ) + -->
<!--   scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1, "***" = 1)) + -->
<!--   scale_linetype_manual(values = c("NS" = "dotted", "*" = "solid", "**" = "solid", "***" = "solid")) + -->
<!--   scale_x_continuous(expand = c(0, 0)) + -->
<!--   scale_color_manual(values = DVs) + -->
<!--   guides(size = "none", linetype = "none", color = "none") + -->
<!--   theme_modern() + -->
<!--   labs(y = "Illusion Sensitivity", title = "Age") + -->
<!--   theme( -->
<!--     legend.position = "top", -->
<!--     axis.title.x = element_blank(), -->
<!--     axis.title.y = element_blank(), -->
<!--     plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5) -->
<!--   ) -->

<!-- p_age -->
<!-- ``` -->



<!-- ## Education -->

<!-- ```{r education_stats, message=FALSE, warning=FALSE, cache=cache} -->
<!-- preds <- data.frame() -->
<!-- for (i in names(DVs)) { -->
<!--   model <- brms::brm(paste0(i, " ~ mo(as.numeric(Education))"), data = filter(dfsub, !Education %in% c("Other", "Prefer not to Say")), refresh = 0) -->
<!--   param <- bayestestR::describe_posterior(as.data.frame(model)["bsp_moas.numericEducation"]) -->

<!--   pred <- estimate_relation(model) -->
<!--   pred$Index <- i -->
<!--   pred$sig <- param$pd -->
<!--   preds <- rbind(preds, pred) -->
<!-- } -->

<!-- preds |> -->
<!--   mutate( -->
<!--     sig = format_pd(sig, stars_only = TRUE), -->
<!--     sig = ifelse(sig == "", "NS", sig) -->
<!--   ) |> -->
<!--   ggplot(aes(x = Education, y = Predicted)) + -->
<!--   geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) + -->
<!--   scale_size_manual(values = c("NS" = 0.5, "*" = 1)) + -->
<!--   scale_linetype_manual(values = c("NS" = "dotted", "*" = "solid")) + -->
<!--   theme_modern() -->
<!-- ``` -->





## Ethnicity {.tabset}

### Illusion

```{r education_stats, message=FALSE, warning=FALSE, cache=cache}
params <- data.frame()
means <- data.frame()
for (i in names(DVs)) {
  # model <- brms::brm(paste0(i, " ~ Ethnicity"), data = filter(dfsub, !Ethnicity %in% c("Other")), refresh = 0)
  model <- lm(paste0(i, " ~ Ethnicity"), data = filter(dfsub, !Ethnicity %in% c("Other")))
  param <- estimate_contrasts(model, contrast="Ethnicity", p_adjust = "holm")
  mean <- estimate_means(model, at="Ethnicity")
  
  param$Index <- i
  param$sig <- param$pd
  params <- rbind(params, param)
  mean$Index <- i
  means <- rbind(means, mean)
}

params |> 
  arrange(p) |> 
  filter(p < .1) |> 
  format_table() |> 
  display()

means |>
  mutate(Index = prettify(Index)) |> 
  ggplot(aes(x = Ethnicity, y = Mean, color = Index, group=Index)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_line(position = position_dodge(width = 0.15)) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.15)) +
  scale_color_manual(values = setNames(DVs, prettify(names(DVs)))) +
  theme_modern() +
  theme(axis.title.x = element_blank())


# params |>
#   mutate(Contrast = paste0(Level1, " - ", Level2),
#          Index = prettify(Index)) |> 
#   ggplot(aes(x = Contrast, y = Difference, color = Index, group=Index)) +
#   geom_hline(yintercept = 0, linetype = "dotted") +
#   geom_line(position = position_dodge(width = 0.1)) +
#   geom_pointrange(aes(ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1)) +
#   scale_color_manual(values = setNames(DVs, prettify(names(DVs)))) +
#   theme_modern() +
#   theme(axis.text.x = element_text(angle= 45, hjust = 1),
#         axis.title.x = element_blank())
```

### Perceptual

```{r education_stats, message=FALSE, warning=FALSE, cache=cache}
params <- data.frame()
means <- data.frame()
for (i in names(DVs_p)) {
  # model <- brms::brm(paste0(i, " ~ Ethnicity"), data = filter(dfsub, !Ethnicity %in% c("Other")), refresh = 0)
  model <- lm(paste0(i, " ~ Ethnicity"), data = filter(dfsub, !Ethnicity %in% c("Other")))
  param <- estimate_contrasts(model, contrast="Ethnicity", p_adjust = "holm")
  mean <- estimate_means(model, at="Ethnicity")
  
  param$Index <- i
  param$sig <- param$pd
  params <- rbind(params, param)
  mean$Index <- i
  means <- rbind(means, mean)
}

params |> 
  arrange(p) |> 
  filter(p < .1) |> 
  format_table() |> 
  display()

means |>
  mutate(Index = prettify(Index)) |> 
  ggplot(aes(x = Ethnicity, y = Mean, color = Index, group=Index)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_line(position = position_dodge(width = 0.15)) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.15)) +
  scale_color_manual(values = setNames(DVs_p, prettify(names(DVs_p)))) +
  theme_modern() +
  theme(axis.title.x = element_blank())
```


# Personality {.tabset}

## IPIP6 {.tabset}

### Illusion

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
ipip <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("IPIP")))
ipip$table
ipip$r
```

### Perceptual

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
ipip_p <- make_correlation(dfsub[names(DVs_p)], select(dfsub, starts_with("IPIP")))
ipip_p$table

plot_correlation(dfsub, x="p_RT", y="IPIP6_Agreeableness", fill="grey")
plot_correlation(dfsub, x="p_RT", y="IPIP6_Openness", fill="grey")
```

## PID-5

### Illusion

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
pid <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("PID")))
pid$table
pid$r
plot(pid$m)
```

### Perceptual

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
pid_p <- make_correlation(dfsub[names(DVs_p)], select(dfsub, starts_with("PID")))
pid_p$table
```

# Psychopathology {.tabset}

## ASQ

```{r, message=FALSE, warning=FALSE}
asq <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("ASQ_")))
asq$table
```

## SPQ

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
spq <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("SPQ_"))) 
spq$table
```

## BPD

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
bpd <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("BPD"))) 
bpd$table
```

## PHQ

```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
phq <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("PHQ4_"))) 
phq$table
```

# Interoception {.tabset}

## IAS 

```{r, message=FALSE, warning=FALSE}
dfsub$IAS_General <- rowMeans(select(dfsub, starts_with("IAS")))
ias <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("IAS")))
ias$table
```

## MAIA

```{r, message=FALSE, warning=FALSE}
maia <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("MAIA")))
maia$table
```

# Other {.tabset}

## Primal Beliefs

```{r, message=FALSE, warning=FALSE}
pi <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("PI_")))
pi$table
```

## Lie Scale

```{r, message=FALSE, warning=FALSE}
lie <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("LIE_")))
lie$table
```

## Conspiracy Beliefs

```{r, message=FALSE, warning=FALSE}
gcbs <- make_correlation(dfsub[names(DVs)], select(dfsub, starts_with("GCBS_")))
gcbs$table
```


# Figure


```{r ipip_stats, message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
data <- rbind(
  mutate(ipip$r, Domain = "Normal Personality"),
  mutate(pid$r, Domain = "Maladaptive Personality"),
  mutate(asq$r, Domain = "Autististic Traits"),
  mutate(spq$r, Domain = "Schizotypic Traits"),
  mutate(bpd$r, Domain = "Mood"),
  mutate(phq$r, Domain = "Mood"),
  filter(mutate(ias$r, Domain = "Interoception"), Parameter2 == "IAS_General"),
  mutate(maia$r, Domain = "Interoception"),
  mutate(gcbs$r, Domain = "Conspiracy Beliefs"),
  mutate(lie$r, Domain = "Lying Profile"),
  mutate(pi$r, Domain = "Primal World Beliefs")
) |> 
  mutate(alpha = case_when(`BF (Spearman)` >= 10 ~ "BF >= 10", `BF (Spearman)` < .01 ~ "BF < 1/10", TRUE ~ "BF < 10"),
         Domain = fct_relevel(Domain, "Normal Personality", "Maladaptive Personality", "Autististic Traits", "Schizotypic Traits", "Mood", "Interoception", "Conspiracy Beliefs", "Lying Profile", "Primal World Beliefs"),
         Parameter1 = prettify(Parameter1),
         Parameter2 = prettify(Parameter2),
         color = paste0(as.character(sign(rho)), Domain)) 

colors <- c(
    "-1Normal Personality" = "#43A047", 
    "1Normal Personality" = "#43A047",
    "-1Maladaptive Personality" = "#00897B", 
    "1Maladaptive Personality" = "#00897B", 
    "-1Autististic Traits" = "#00BCD4",
    "1Autististic Traits" = "#00BCD4", 
    "-1Schizotypic Traits" = "#03A9F4",
    "1Schizotypic Traits" = "#03A9F4", 
    "-1Mood" = "#2196F3", 
    "1Mood" = "#2196F3",
    "-1Interoception" = "#F44336", 
    "1Interoception" = "#F44336",
    "-1Conspiracy Beliefs" = "#9C27B0", 
    "1Conspiracy Beliefs" = "#9C27B0",
    "-1Lying Profile" = "#3F51B5", 
    "1Lying Profile" = "#3F51B5",
    "-1Primal World Beliefs" = "#FFC107", 
    "1Primal World Beliefs" = "#FFC107")

p_cor <- data |>
  mutate(Parameter2 = fct_relevel(Parameter2, arrange(filter(data, Parameter1 == "Perception (Attention)"), Domain, rho)[["Parameter2"]])) |>
  ggplot(aes(x = rho, y = Parameter2)) +
  geom_bar(aes(alpha = alpha, fill = color), stat = "identity") +
  geom_linerange(aes(alpha = alpha, xmin = CI_low, xmax = CI_high, color = color)) +
  geom_vline(xintercept = 0) +
  facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
  scale_alpha_manual(values = c(0.2, 0.9), guide="none") +
  scale_colour_manual(values = colors, guide="none") +
  scale_fill_manual(values = colors, guide="none") +
  scale_x_continuous(expand = c(0, 0), breaks = seq(-0.2, 0.2, by=0.1)) +
  coord_cartesian(xlim = c(-0.3, 0.3)) +
  labs(title = "Correlation with Dispositional Traits") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(size = rel(1.5), face = "bold", hjust = 0.5),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement.y = "outside",
        strip.background.x = element_rect(fill = "#E0E0E0", color = "white"),
        strip.text.x = element_text(face = "bold", size = rel(1.1)),
        strip.text.y = element_text(face = "bold", size = rel(0.95)))
p_cor

# Final plot
load_plot <- function(x) patchwork::wrap_elements(grid::rasterGrob(png::readPNG(x), interpolate = TRUE))

p_demo <- (
  load_plot("figures/1_Preprocessing-p_demographics_country-1.png") |
    load_plot("figures/1_Preprocessing-p_demographics_age-1.png") | 
  load_plot("figures/1_Preprocessing-p_demographics_ethnicity-1.png") |
    load_plot("figures/1_Preprocessing-p_demographics_education-1.png")
) + plot_annotation(title = "Demographic Information", subtitle = "N = 497 (49.9% ♀)",
                    theme = theme(plot.title = element_text(size = rel(1.5), face = "bold", hjust = 0.5),
                                  plot.subtitle = element_text(size = rel(1.1), face = "italic", hjust = 0.5)))
p_demo


# p_demo <- patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_demographics.png"), interpolate = TRUE))
p <- (patchwork::wrap_elements(p_demo) / 
        patchwork::wrap_elements(patchwork::wrap_elements(p_cor + theme(plot.title = element_blank())) + plot_annotation(
          title = "Correlation with Dispositional Traits", 
          theme = theme(plot.title = element_text(size = rel(1.5), face = "bold", hjust = 0.5))))
      ) + plot_layout(heights = c(1/4, 3/4))
ggsave("figures/figure_correlations.png", p, width = 12 * sqrt(2), height=12 * sqrt(2), dpi=150)
```


